Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-19 papers/B1555_EdgeOn/B1555_letter.tex
minor change in table, add ref to bib file

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
\usepackage[nottoc]{tocbibind}

@@

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14b}.

@@

\hline
	& \multicolumn{2}{c}{MERLIN} & \multicolumn{3}{c}{Model}\\
		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
A/B			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
A/C 		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
A/D			&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
%\usepackage[nottoc]{tocbibind}

@@

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure.

An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

@@

\hline
	& MERLIN & VLA & \multicolumn{3}{c}{Model}\\
		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
A/B			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
A/C 		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
A/D			&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\
